Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2023-01-25 Thesis/chapter/061-results-emma.tex
add pre-emma table to appendix

%%% OVER TIME 
The only clear trend from table \ref{tab:emma-Gb} is the layer count, which rises with the generations. 
The remaining input variables remained more or less the same except for the 3rd generation. 
\td{why?}
%
In table \ref{tab:emma-pred-G} it can be seen that the predicted $\hat{\gamma}$ 
(predicted with 5th generation \gls{rf}; see last column) lowered with each iteration, 
except for sample 2947, which wasn't predicted but measured. 
This shows that the easiest part of the algorithm - the selection of the optimum 
from predicted values - works as expected. 
% and that the predictions included more lower values over time
%
Contrarily, the predicted $\hat{\gamma}$ for each generation's best 
(predicted by the very generation's \gls{rf}) does increase with each iteration 
(see diagonal in table~\ref{tab:emma-pred-G}). 
This indicates an underestimation of $\hat\gamma$ at the beginning and a correction with time. 
%The reason for is probably a 
The underestimation probably stems from a lucky selection of initial experiments or a skew in the measurements. 
Indeed, the samples with the lowest \textit{optimisands} are amoung the first generation (see appendix \ref{sec:app-emma}, \td{and maybe fig gen-g}).

@@

\begin{figure}[hb]
    \centering
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/gen-G.png}
        \caption{} \label{fig:emma-G-gen}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/gen-phd.png}
        \caption{} \label{fig:emma-phd-gen}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/G-tcal.png}
        \caption{} \label{fig:g-tcal}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/phd-tcal.png}
        \caption{} \label{fig:phd-tcal}
    \end{subfigure}
	\caption{$\gamma$ (a) and of $\rho$ (b) of each particle and each generation after initial selection process; \td{add caption for c and d. check if can plot with t=0}} 
    \label{fig:emma-gen}
\end{figure}

>>>>

%%% OVER TIME 
The only clear trend from table \ref{tab:emma-Gb} is the layer count, which rises with the generations. 
The remaining input variables remained more or less the same except for the 3rd generation. 
\td{why?}
%
In table \ref{tab:emma-pred-G} it can be seen that the predicted $\hat{\gamma}$ 
(predicted with 5th generation \gls{rf}; see last column) lowered with each iteration, 
except for sample 2947, which wasn't predicted but measured. 
This shows that the easiest part of the algorithm - the selection of the optimum 
from predicted values - works as expected. 
% and that the predictions included more lower values over time
%
Contrarily, the predicted $\hat{\gamma}$ for each generation's best 
(predicted by the very generation's \gls{rf}) does increase with each iteration 
(see diagonal in table~\ref{tab:emma-pred-G}). 
This indicates an underestimation of $\hat\gamma$ at the beginning and a correction with time. 
%The reason for is probably a 
The underestimation probably stems from a lucky selection of initial experiments or a skew in the measurements. 
Indeed, the samples with the lowest \textit{optimisands} are amoung the first generation (see figure \ref{fig:emma-G-gen}, figure \ref{fig:emma-phd-gen} and appendix \ref{sec:app-emma}).

@@

\begin{figure}[hb]
    \centering
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/gen-G.png}
        \caption{} \label{fig:emma-G-gen}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/gen-phd.png}
        \caption{} \label{fig:emma-phd-gen}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/G-tcal.png}
        \caption{} \label{fig:g-tcal}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/phd-tcal.png}
        \caption{} \label{fig:phd-tcal}
    \end{subfigure}
	\caption{$\gamma$ (a) and of $\rho$ (b) of each particle and each generation after initial selection process; \td{add caption for c and d.}} 
    \label{fig:emma-gen}
\end{figure}
